In this project, Nvidia Jetson TX1 embedded platform will be used for power and performance analysis. We will run various deep neural network architectures for image classification task on GPU. We will use small, medium, and large deep neural networks to make a thorough power and performance analysis with different network characteristics. Caffe framework \cite{caffe} will be used to implement deep neural networks on GPU. Similarly, we will use SPLASH2 benchmark suite \cite{woo1995splash} for CPU. Various SPLASH2 benchmarks will be used to cover different workload characteristics such as memory-intensive and compute-intensive workloads. Furthermore, we will run these CPU-GPU benchmarks with using three different frequency values for both CPU and GPU. First, we will run them individually to obtain power, performance, and temperature results for the baseline. Secondly, we will run them jointly to do analysis and optimization for deep learning on embedded CPU-GPU platforms.

Power values will be calculated by using current sensors in Nvidia Jetson TX1 platform. Temperature results also will be collected by using thermal sensors in TX1. We may also take off the heat sink to simulate embedded platforms which do not have heat sink. It will significantly increase temperature values. However, CPU and GPU will throttle themselves to not exceed thermal design power (TDP) constraint. Performance results for CPU will be calculated by using performance counters as an instruction per cycle (IPC) metric. Moreover, we will obtain CPU utilization results using system calls. Execution time of deep neural network will be calculated using Caffe framework as a performance metric. 
